---
title: "Upsetplot - deseq 1"
output: html_notebook
---

setup
```{r}
library(tidyverse)
#install.packages("UpSetR")
library(UpSetR)
library(reshape2)

```


working directory
```{r}
setwd("/Users/annenakamoto/ROTATION2/DESEQ2/DE_GENES")
list.files()
```

download data
```{r}
DE_GENES <- read_tsv("ALL.DEgenes.tsv")

### combine the species and tissue columns
DE_GENES$species_tissue <- paste(DE_GENES$species, DE_GENES$tissue, sep=":")
DE_GENES

### ALL
DE_GENES.all <- DE_GENES[is.numeric(DE_GENES$log2FoldChange),]  ## all
DE_GENES.all
DE_GENES.all <- DE_GENES.all[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.all <- dcast(DE_GENES.all, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.all <- DE_GENES.all[complete.cases(DE_GENES.all), ]         ## remove NA OGs
DE_GENES.all <- DE_GENES.all %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.all[DE_GENES.all>0] <-1   ## p/a matrix
DE_GENES.all

### Upregulated
DE_GENES.up <- DE_GENES[DE_GENES$log2FoldChange > 0,]  ## filter for upregulated
DE_GENES.up
DE_GENES.up <- DE_GENES.up[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.up <- dcast(DE_GENES.up, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.up <- DE_GENES.up[complete.cases(DE_GENES.up), ]         ## remove NA OGs
DE_GENES.up <- DE_GENES.up %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.up[DE_GENES.up>0] <-1   ## p/a matrix
DE_GENES.up

### Downregulated
DE_GENES.dn <- DE_GENES[DE_GENES$log2FoldChange < 0,]  ## filter for downregulated
DE_GENES.dn
DE_GENES.dn <- DE_GENES.dn[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.dn <- dcast(DE_GENES.dn, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.dn <- DE_GENES.dn[complete.cases(DE_GENES.dn), ]         ## remove NA OGs
DE_GENES.dn <- DE_GENES.dn %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.dn[DE_GENES.dn>0] <-1   ## p/a matrix
DE_GENES.dn

```

Specify different groupings of species-tissue sets
```{r}
### All species
all_sp <- c("brown_bear:adipose", "brown_bear:liver", "brown_bear:muscle", "black_bear:bone", "dwarf_lemur:white_adipose", 
            "greater_horseshoe_bat:intestine", "brandts_bat:brain", "brandts_bat:kidney", "brandts_bat:liver",
            "syrian_hamster:white_adipose", "djungarian_hamster:blood", "arctic_ground_squirrel:muscle", 
            "13_lined_ground_squirrel:cerebrum", "13_lined_ground_squirrel:hypothalamus", "13_lined_ground_squirrel:medulla",
            "monito_del_monte:muscle", "monito_del_monte:liver", "monito_del_monte:brain")

## by species
bear_subset <- c("black_bear:bone", "brown_bear:adipose", "brown_bear:liver", "brown_bear:muscle")
bat_subset <- c("brandts_bat:brain", "brandts_bat:kidney", "brandts_bat:liver", "greater_horseshoe_bat:intestine")
smallMammal_subset <- c("13_lined_ground_squirrel:cerebrum", "13_lined_ground_squirrel:hypothalamus", "13_lined_ground_squirrel:medulla", 
                        "arctic_ground_squirrel:muscle", "djungarian_hamster:blood", "syrian_hamster:white_adipose", "dwarf_lemur:white_adipose")
monito_subset <- c("monito_del_monte:muscle", "monito_del_monte:liver", "monito_del_monte:brain")

## by tissue
adipose_subset <- c("brown_bear:adipose", "dwarf_lemur:white_adipose", "syrian_hamster:white_adipose")
liver_subset <- c("brown_bear:liver", "brandts_bat:liver", "monito_del_monte:liver")
muscle_subset <- c("brown_bear:muscle", "arctic_ground_squirrel:muscle", "monito_del_monte:muscle")
brain_subset <- c("13_lined_ground_squirrel:cerebrum", "13_lined_ground_squirrel:hypothalamus", "13_lined_ground_squirrel:medulla", "brandts_bat:brain", "monito_del_monte:brain")

tissue_sets <- c(adipose_subset,liver_subset,muscle_subset)

## by clade in phylogeny
bear_bat_subset <- c(bear_subset, bat_subset)
lemur_squirrel_hamster_subset <- smallMammal_subset

```

Upset plots (ALL species)
```{r}
png("ALL_species.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.mat, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("ALL_species.UP.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.up, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("ALL_species.DOWN.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.dn, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 
```

Upset plots (Adipose)
```{r}
png("adipose_subset.upset.png", width = 5, height = 4, units = "in", res = 300)
u1 <- upset(DE_GENES.mat, sets = rev(adipose_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u1
dev.off()

png("adipose_subset.UP.upset.png", width = 5, height = 4, units = "in", res = 300)
u2 <- upset(DE_GENES.up, sets = rev(adipose_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u2
dev.off()

png("adipose_subset.DOWN.upset.png", width = 5, height = 4, units = "in", res = 300)
u3 <- upset(DE_GENES.dn, sets = rev(adipose_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u3
dev.off() 
```


Upset plots (liver_subset)
```{r}
png("liver_subset.upset.png", width = 5, height = 4, units = "in", res = 300)
u1 <- upset(DE_GENES.mat, sets = rev(liver_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u1
dev.off()

png("liver_subset.UP.upset.png", width = 5, height = 4, units = "in", res = 300)
u2 <- upset(DE_GENES.up, sets = rev(liver_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u2
dev.off()

png("liver_subset.DOWN.upset.png", width = 5, height = 4, units = "in", res = 300)
u3 <- upset(DE_GENES.dn, sets = rev(liver_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u3
dev.off() 
```

Upset plots (muscle_subset)
```{r}
png("muscle_subset.upset.png", width = 5, height = 4, units = "in", res = 300)
u1 <- upset(DE_GENES.mat, sets = rev(muscle_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u1
dev.off()

png("muscle_subset.UP.upset.png", width = 5, height = 4, units = "in", res = 300)
u2 <- upset(DE_GENES.up, sets = rev(muscle_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u2
dev.off()

png("muscle_subset.DOWN.upset.png", width = 5, height = 4, units = "in", res = 300)
u3 <- upset(DE_GENES.dn, sets = rev(muscle_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u3
dev.off() 
```

Upset plots (brain_subset)
```{r}
png("brain_subset.upset.png", width = 7, height = 4, units = "in", res = 300)
u1 <- upset(DE_GENES.mat, sets = rev(brain_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u1
dev.off()

png("brain_subset.UP.upset.png", width = 7, height = 4, units = "in", res = 300)
u2 <- upset(DE_GENES.up, sets = rev(brain_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u2
dev.off()

png("brain_subset.DOWN.upset.png", width = 7, height = 4, units = "in", res = 300)
u3 <- upset(DE_GENES.dn, sets = rev(brain_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 0, text.scale = c(1.2, 1.2, 1.2, 1, 1.2, 0.75),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u3
dev.off() 
```

SPLIT:
  - OGs with at least one gene from each species (noZERO)
  - OGs with zero genes from one or more species (ZEROs)
```{r}
DE_GENES.noZ <- read_tsv("ALL.DEgenes.noZERO.tsv")
DE_GENES.Zs <- read_tsv("ALL.DEgenes.ZEROs.tsv")

### combine the species and tissue columns
DE_GENES.noZ$species_tissue <- paste(DE_GENES.noZ$species, DE_GENES.noZ$tissue, sep=":")
DE_GENES.Zs$species_tissue <- paste(DE_GENES.Zs$species, DE_GENES.Zs$tissue, sep=":")

### ALL
DE_GENES.noZ.all <- DE_GENES.noZ[is.numeric(DE_GENES.noZ$log2FoldChange),]  ## all
DE_GENES.noZ.all
DE_GENES.noZ.all <- DE_GENES.noZ.all[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.noZ.all <- dcast(DE_GENES.noZ.all, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.noZ.all <- DE_GENES.noZ.all[complete.cases(DE_GENES.noZ.all), ]         ## remove NA OGs
DE_GENES.noZ.all <- DE_GENES.noZ.all %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.noZ.all[DE_GENES.noZ.all>0] <-1   ## p/a matrix
DE_GENES.noZ.all

DE_GENES.Zs.all <- DE_GENES.Zs[is.numeric(DE_GENES.Zs$log2FoldChange),]  ## all
DE_GENES.Zs.all
DE_GENES.Zs.all <- DE_GENES.Zs.all[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.Zs.all <- dcast(DE_GENES.Zs.all, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.Zs.all <- DE_GENES.Zs.all[complete.cases(DE_GENES.Zs.all), ]         ## remove NA OGs
DE_GENES.Zs.all <- DE_GENES.Zs.all %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.Zs.all[DE_GENES.Zs.all>0] <-1   ## p/a matrix
DE_GENES.Zs.all

### Upregulated
DE_GENES.noZ.up <- DE_GENES.noZ[DE_GENES.noZ$log2FoldChange > 0,]  ## filter for upregulated
DE_GENES.noZ.up
DE_GENES.noZ.up <- DE_GENES.noZ.up[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.noZ.up <- dcast(DE_GENES.noZ.up, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.noZ.up <- DE_GENES.noZ.up[complete.cases(DE_GENES.noZ.up), ]         ## remove NA OGs
DE_GENES.noZ.up <- DE_GENES.noZ.up %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.noZ.up[DE_GENES.noZ.up>0] <-1   ## p/a matrix
DE_GENES.noZ.up

DE_GENES.Zs.up <- DE_GENES.Zs[DE_GENES.Zs$log2FoldChange > 0,]  ## filter for upregulated
DE_GENES.Zs.up
DE_GENES.Zs.up <- DE_GENES.Zs.up[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.Zs.up <- dcast(DE_GENES.Zs.up, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.Zs.up <- DE_GENES.Zs.up[complete.cases(DE_GENES.Zs.up), ]         ## remove NA OGs
DE_GENES.Zs.up <- DE_GENES.Zs.up %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.Zs.up[DE_GENES.Zs.up>0] <-1   ## p/a matrix
DE_GENES.Zs.up

### Downregulated
DE_GENES.noZ.dn <- DE_GENES.noZ[DE_GENES.noZ$log2FoldChange < 0,]  ## filter for downregulated
DE_GENES.noZ.dn
DE_GENES.noZ.dn <- DE_GENES.noZ.dn[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.noZ.dn <- dcast(DE_GENES.noZ.dn, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.noZ.dn <- DE_GENES.noZ.dn[complete.cases(DE_GENES.noZ.dn), ]         ## remove NA OGs
DE_GENES.noZ.dn <- DE_GENES.noZ.dn %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.noZ.dn[DE_GENES.noZ.dn>0] <-1   ## p/a matrix
DE_GENES.noZ.dn

DE_GENES.Zs.dn <- DE_GENES.Zs[DE_GENES.Zs$log2FoldChange < 0,]  ## filter for downregulated
DE_GENES.Zs.dn
DE_GENES.Zs.dn <- DE_GENES.Zs.dn[, c("species_tissue", "Orthogroup")]   ## reduce columns
DE_GENES.Zs.dn <- dcast(DE_GENES.Zs.dn, Orthogroup ~ species_tissue)    ## reshape to wide
DE_GENES.Zs.dn <- DE_GENES.Zs.dn[complete.cases(DE_GENES.Zs.dn), ]         ## remove NA OGs
DE_GENES.Zs.dn <- DE_GENES.Zs.dn %>% column_to_rownames('Orthogroup')   ## OG rownames
DE_GENES.Zs.dn[DE_GENES.Zs.dn>0] <-1   ## p/a matrix
DE_GENES.Zs.dn
```


Upset plots (ALL species, noZERO and ZEROs)
```{r}
######## noZERO ########

png("ALL_species.noZERO.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.noZ.all, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("ALL_species.noZERO.UP.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.noZ.up, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("ALL_species.noZERO.DOWN.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.noZ.dn, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 


######## ZEROs ########

png("ALL_species.ZEROs.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.all, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("ALL_species.ZEROs.UP.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.up, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("ALL_species.ZEROs.DOWN.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.dn, sets = rev(all_sp), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 
```


Upset plots (separated by clade for ZEROs subset)
bear_bat_subset
lemur_squirrel_hamster_subset
```{r}
####### bear_bat #######

png("bear_bat.ZEROs.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.all, sets = rev(bear_bat_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("bear_bat.ZEROs.UP.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.up, sets = rev(bear_bat_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("bear_bat.ZEROs.DOWN.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.dn, sets = rev(bear_bat_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 


####### lemur_squirrel_hamster #######

png("lemur_squirrel_hamster.ZEROs.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.all, sets = rev(lemur_squirrel_hamster_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("lemur_squirrel_hamster.ZEROs.UP.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.up, sets = rev(lemur_squirrel_hamster_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

png("lemur_squirrel_hamster.ZEROs.DOWN.upset.png", width = 9, height = 4, units = "in", res = 300)
u <- upset(DE_GENES.Zs.dn, sets = rev(lemur_squirrel_hamster_subset), keep.order = TRUE, nsets=18, order.by = c("freq"), 
           mb.ratio = c(0.5, 0.5), number.angles = 20, text.scale = c(1, 1, 1, 1, 1, 0.5),
           mainbar.y.label = "Orthogroup intersection size", sets.x.label = "DE orthogroup count", nintersects = 60)
u
dev.off() 

```


